BANTER for Beaked Whales: South Atlantic

### 2024-01-30 satlantic/beakerBanter_satlantic.Rmd
Revisions and Rebuttal
Revisions to manuscript + Rebuttal draft

```{r, load packages, message=FALSE}
library("easypackages")
libraries("PAMpal", "banter", "rfPermute", "kableExtra", "readxl", "stringr", "magick", "magrittr", "here")
here()
```

@@

```{r, proximity plot, include=TRUE, results=FALSE}
png(('../manuscript/manuscript_files/satlantic_ec_proximity.png'), width = 20, height = 20, units = 'cm', res = 300)
satlantic_ec_proximityPlot <- plotProximity(banter_model_ec_RF)
dev.off()
satlantic_ec_proximityPlot <- plotProximity(banter_model_ec_RF)

png(('../manuscript/manuscript_files/satlantic_ici_proximity.png'), width = 20, height = 20, units = 'cm', res = 300)
ici_satlantic_proximityPlot <- plotProximity(banter_model_ici_RF)
dev.off()
ici_satlantic_proximityPlot <- plotProximity(banter_model_ici_RF)

png(('../manuscript/manuscript_files/satlantic_env_proximity.png'), width = 20, height = 20, units = 'cm', res = 300)
env_satlantic_proximityPlot <- plotProximity(banter_model_env_RF)
dev.off()
env_satlantic_proximityPlot <- plotProximity(banter_model_env_RF)

png(('../manuscript/manuscript_files/satlantic_alt_proximity.png'), width = 20, height = 20, units = 'cm', res = 300)
alt_satlantic_proximityPlot <- plotProximity(banter_model_alt_RF)
dev.off()
alt_satlantic_proximityPlot <- plotProximity(banter_model_alt_RF)
```

@@

```{r, importance heat map, include=TRUE, results=FALSE}
png(('../manuscript/manuscript_files/satlantic_ec_importance.png'), width = 30, height = 25, units = 'cm', res = 300)
plotImportance(banter_model_ec_RF, plot.type="heatmap", n=10)
dev.off()
satlantic_importance <- plotImportance(banter_model_ec_RF, plot.type="heatmap", n=10)

png(('../manuscript/manuscript_files/satlantic_ici_importance.png'), width = 30, height = 25, units = 'cm', res = 300)
plotImportance(banter_model_ici_RF, plot.type="heatmap", n=10)
dev.off()
ici_satlantic_importance <- plotImportance(banter_model_ici_RF, plot.type="heatmap", n=10)

png(('../manuscript/manuscript_files/satlantic_env_importance.png'), width = 30, height = 25, units = 'cm', res = 300)
plotImportance(banter_model_env_RF, plot.type="heatmap", n=10)
dev.off()
env_satlantic_importance <- plotImportance(banter_model_env_RF, plot.type="heatmap", n=10)

png(('../manuscript/manuscript_files/satlantic_alt_importance.png'), width = 30, height = 25, units = 'cm', res = 300)
plotImportance(banter_model_alt_RF, plot.type="heatmap", n=10)
dev.off()
alt_satlantic_importance <- plotImportance(banter_model_alt_RF, plot.type="heatmap", n=10)
```

@@

```{r, plot votes, include=TRUE, results=FALSE}
png(('../manuscript/manuscript_files/satlantic_ec_votes.png'), width = 20, height = 20, units = 'cm',  res = 300)
plotVotes(banter_model_ec_RF)
dev.off()
satlantic_votes <- plotVotes(banter_model_ec_RF)

png(('../manuscript/manuscript_files/satlantic_ici_votes.png'), width = 20, height = 20, units = 'cm',  res = 300)
plotVotes(banter_model_ici_RF)
dev.off()
ici_satlantic_votes <- plotVotes(banter_model_ici_RF)

png(('../manuscript/manuscript_files/satlantic_env_votes.png'), width = 20, height = 20, units = 'cm',  res = 300)
plotVotes(banter_model_env_RF)
dev.off()
env_satlantic_votes <- plotVotes(banter_model_env_RF)

png(('../manuscript/manuscript_files/satlantic_alt_votes.png'), width = 20, height = 20, units = 'cm',  res = 300)
plotVotes(banter_model_alt_RF)
dev.off()
alt_satlantic_votes <- plotVotes(banter_model_alt_RF)
```

@@

Create Figure for Publication
```{r, Publication Figure, include=TRUE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=300, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=300, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=300, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=300, color = "black")

@@

confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ici_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=300, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ici_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=300, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ici_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=300, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ici_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=300, color = "black")

@@

confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_env_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_env_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_env_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_env_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

>>>>

```{r, load packages, message=FALSE}
library("easypackages")
libraries("PAMpal", "banter", "rfPermute", "kableExtra", "readxl", "stringr", "magick", "magrittr", "ggplot2", "here")
here()
```

@@

```{r, proximity plot, include=TRUE, results=FALSE}
png(('../manuscript/manuscript_files/satlantic_ec_proximity.png'), width = 20, height = 20, units = 'cm', res = 300)
ec_satlantic_proximityPlot <- plotProximity(banter_model_ec_RF, plot = FALSE)
ec_satlantic_proximityPlot$g + theme(axis.text = element_text(size = 16),
                                     axis.title = element_text(size = 16),
                                     legend.text = element_text(size = 16)
                                     )
dev.off()
satlantic_ec_proximityPlot <- plotProximity(banter_model_ec_RF)

png(('../manuscript/manuscript_files/satlantic_ici_proximity.png'), width = 20, height = 20, units = 'cm', res = 300)
ici_satlantic_proximityPlot <- plotProximity(banter_model_ici_RF, plot = FALSE)
ici_satlantic_proximityPlot$g + theme(axis.text = element_text(size = 16),
                                     axis.title = element_text(size = 16),
                                     legend.text = element_text(size = 16)
                                     )
dev.off()
ici_satlantic_proximityPlot <- plotProximity(banter_model_ici_RF)

png(('../manuscript/manuscript_files/satlantic_env_proximity.png'), width = 20, height = 20, units = 'cm', res = 300)
env_satlantic_proximityPlot <- plotProximity(banter_model_env_RF, plot = FALSE)
env_satlantic_proximityPlot$g + theme(axis.text = element_text(size = 16),
                                     axis.title = element_text(size = 16),
                                     legend.text = element_text(size = 16)
                                     )
dev.off()
env_satlantic_proximityPlot <- plotProximity(banter_model_env_RF)

png(('../manuscript/manuscript_files/satlantic_alt_proximity.png'), width = 20, height = 20, units = 'cm', res = 300)
alt_satlantic_proximityPlot <- plotProximity(banter_model_alt_RF, plot = FALSE)
alt_satlantic_proximityPlot$g + theme(axis.text = element_text(size = 16),
                                     axis.title = element_text(size = 16),
                                     legend.text = element_text(size = 16)
                                     )
dev.off()
alt_satlantic_proximityPlot <- plotProximity(banter_model_alt_RF)
```

@@

```{r, importance heat map, include=TRUE, results=FALSE}
png(('../manuscript/manuscript_files/satlantic_ec_importance.png'), width = 30, height = 25, units = 'cm', res = 300)
ec_satlantic_plotImportance <- plotImportance(banter_model_ec_RF, plot.type="heatmap",n=10, plot = FALSE)
ec_satlantic_plotImportance + theme(axis.text = element_text(size = 16),
                                      axis.text.x = element_text(angle = -30, vjust = 1, hjust = 0),
                                      legend.text = element_text(size = 16)
                                      )
dev.off()
satlantic_importance <- plotImportance(banter_model_ec_RF, plot.type="heatmap", n=10)

png(('../manuscript/manuscript_files/satlantic_ici_importance.png'), width = 30, height = 25, units = 'cm', res = 300)
ici_satlantic_plotImportance <- plotImportance(banter_model_ici_RF, plot.type="heatmap",n=10, plot = FALSE)
ici_satlantic_plotImportance + theme(axis.text = element_text(size = 16),
                                      axis.text.x = element_text(angle = -30, vjust = 1, hjust = 0),
                                      legend.text = element_text(size = 16)
                                      )
dev.off()
ici_satlantic_importance <- plotImportance(banter_model_ici_RF, plot.type="heatmap", n=10)

png(('../manuscript/manuscript_files/satlantic_env_importance.png'), width = 30, height = 25, units = 'cm', res = 300)
env_satlantic_plotImportance <- plotImportance(banter_model_env_RF, plot.type="heatmap",n=10, plot = FALSE)
env_satlantic_plotImportance + theme(axis.text = element_text(size = 16),
                                      axis.text.x = element_text(angle = -30, vjust = 1, hjust = 0),
                                      legend.text = element_text(size = 16)
                                      )
dev.off()
env_satlantic_importance <- plotImportance(banter_model_env_RF, plot.type="heatmap", n=10)

png(('../manuscript/manuscript_files/satlantic_alt_importance.png'), width = 30, height = 25, units = 'cm', res = 300)
alt_satlantic_plotImportance <- plotImportance(banter_model_alt_RF, plot.type="heatmap",n=10, plot = FALSE)
alt_satlantic_plotImportance + theme(axis.text = element_text(size = 16),
                                      axis.text.x = element_text(angle = -30, vjust = 1, hjust = 0),
                                      legend.text = element_text(size = 16)
                                      )
dev.off()
alt_satlantic_importance <- plotImportance(banter_model_alt_RF, plot.type="heatmap", n=10)
```

@@

```{r, plot votes, include=TRUE, results=FALSE}
png(('../manuscript/manuscript_files/satlantic_ec_votes.png'), width = 20, height = 20, units = 'cm',  res = 300)
ec_satlantic_plotVotes <- plotVotes(banter_model_ec_RF, plot = FALSE)
ec_satlantic_plotVotes + theme(axis.text = element_text(size = 16),
                                     axis.title = element_text(size = 16),
                                     legend.text = element_text(size = 16)
                                     )
dev.off()
satlantic_votes <- plotVotes(banter_model_ec_RF)

png(('../manuscript/manuscript_files/satlantic_ici_votes.png'), width = 20, height = 20, units = 'cm',  res = 300)
ici_satlantic_plotVotes <- plotVotes(banter_model_ici_RF, plot = FALSE)
ici_satlantic_plotVotes + theme(axis.text = element_text(size = 16),
                                     axis.title = element_text(size = 16),
                                     legend.text = element_text(size = 16)
                                     )
dev.off()
ici_satlantic_votes <- plotVotes(banter_model_ici_RF)

png(('../manuscript/manuscript_files/satlantic_env_votes.png'), width = 20, height = 20, units = 'cm',  res = 300)
env_satlantic_plotVotes <- plotVotes(banter_model_env_RF, plot = FALSE)
env_satlantic_plotVotes + theme(axis.text = element_text(size = 16),
                                     axis.title = element_text(size = 16),
                                     legend.text = element_text(size = 16)
                                     )
dev.off()
env_satlantic_votes <- plotVotes(banter_model_env_RF)

png(('../manuscript/manuscript_files/satlantic_alt_votes.png'), width = 20, height = 20, units = 'cm',  res = 300)
alt_satlantic_plotVotes <- plotVotes(banter_model_alt_RF, plot = FALSE)
alt_satlantic_plotVotes + theme(axis.text = element_text(size = 16),
                                     axis.title = element_text(size = 16),
                                     legend.text = element_text(size = 16)
                                     )
dev.off()
alt_satlantic_votes <- plotVotes(banter_model_alt_RF)
```

@@

Create Figure for Publication
```{r, Publication Figure, include=TRUE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x200")%>%
  image_annotate("a) Confusion Matrix", size=150, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=150, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=150, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x200")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=150, color = "black")

@@

confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ici_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x200")%>%
  image_annotate("a) Confusion Matrix", size=150, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ici_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=150, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ici_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=150, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ici_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x200")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=150, color = "black")

@@

confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_env_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x200")%>%
  image_annotate("a) Confusion Matrix", size=150, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_env_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=150, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_env_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=150, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_env_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x200")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=150, color = "black")

@@

confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x200")%>%
  image_annotate("a) Confusion Matrix", size=150, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=150, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=150, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x200")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=150, color = "black")
